\section{Introduction}

The lithium-ion battery is the predominant form of commercial rechargeable battery, and is widely used in many applications ranging from consumer electronics to electric vehicles and grid storage. Accurately predicting battery end-of-life (EoL), typically defined as the point at which its capacity falls below a specified threshold, is important for ensuring safety, optimizing maintenance schedules, and enabling efficient lifecycle management. However, battery degradation is influenced by a complex interplay of factors such as usage patterns, environmental conditions, and manufacturing variability, leading to substantial heterogeneity across cells and operating groups.

Traditional data-driven approaches to EoL prediction, such as linear regression or machine learning models, often treat all observations as independent and identically distributed. While these models can achieve reasonable predictive performance, they may fail to capture structured variability across groups, such as differences between batches of cells or operating regimes. Recent work has emphasized the importance of incorporating domain structure and uncertainty into predictive models for battery health, particularly in settings with limited data per group or high variability across populations \cite{severson2019}.

In this project, we investigate a hierarchical Bayesian model (HBM) for predicting battery EoL that explicitly accounts for group-level heterogeneity following methodology from Zhou et al. \cite{ZHOU20236117}. The hierarchical framework allows regression coefficients to vary across groups while sharing statistical strength through common hyperpriors, resulting in a form of partial pooling. This is especially advantageous in battery datasets, where some groups may have few observations but still benefit from information learned across the entire population.